\documentclass[margin,line]{resume}
\usepackage[pdfborderstyle=0 0 0]{hyperref}
\begin{document}
\name{\Large John Bender}
\begin{resume}

  % Contact Information
  \section{\mysidestyle Contact\\Information}

  6109 Melvil St.                       \hfill phone: +1 917 504 3095\\
  Culver City, California 90232         \hfill email: john.m.bender@gmail.com

  % Research Interests
  \section{\mysidestyle Research\\Interests}

  Formal Verification, Software Model Checking, Type Systems, Static Analysis, Applied Mathematics

  % Education
  \section{\mysidestyle Education}

  \textbf{University of Hawai'i at Manoa}, Honolulu, Hawai'i, United States \vspace{2mm}\\
  \textsl{Bachelors of Science}, Computer Science \hfill \textbf{ August 2001 -- May 2006}\vspace{-3mm}\\

  % Professional Experience
  \section{\mysidestyle Professional\\Experience}

  \textbf{Adobe Systems}, San Francisco, California, United States \vspace{1mm}\\
  \textsl{Senior Computer Scientist} \hfill \textbf{July 2011 -- present}\\
  Senior software engineer focused on the jQuery Mobile open source JavaScript library. Contributed to project guidance/management, code base, build support, test suite, and operations.

  \textbf{Originate Labs}, Los Angeles, California, United States \vspace{1mm}\\
  \textsl{Tech Lead, Director of Engineering} \hfill \textbf{August 2009 -- July 2011}\\
  Senior staff member focused on management process, tools, research, development practices, project oversight and hiring practices.

  \textbf{The Henson Group}, New York City, New York, United States \vspace{1mm}\\
  \textsl{Software Consultant} \hfill \textbf{November 2007 -- August 2009}\\
  Specialized in .NET technology stack working for a diverse client set including hedge funds and large multinational corporations like Weight Watchers.

  \section{\mysidestyle Publications}
  Bender, J., ``Automatically Identifying Performance Optimizations in jQuery Based JavaScript Applications'', \textsl{unpublished}, Identifying a set of morphisms via category theory that can be composed leading to loop fusion, \href{http://johnbender.us/auto-js.pdf}{\texttt{www.johnbender.us}}

  \section{\mysidestyle Presentations}
  Bender, J., ``Progressive Enhancement on the Mobile Web'', \textsl{O'Reilly Open Source Convention}, The pitfalls of modern mobile browser fragmentation, July 19th, 2012.\vspace{2mm}\\
  Bender, J., ``Faster jQuery with Category Theory'', \textsl{jQuery Conference San Francisco}, How category theory can be used to identify performance optimizations in jQuery, June 29th, 2012. \vspace{2mm}\\
  Bender, J., ``Middleware as a General Purpose Abstraction'', \textsl{Los Angeles Ruby Conference}, Novel form of object composition derived from WSGI middleware, April 19th, 2012, \href{http://www.youtube.com/watch?feature=player_embedded&v=fcNaiP5tea0}{\texttt{www.youtube.com}}\ \vspace{2mm}\\
  Bender, J., ``JavaScript Testing with JavaScript'', \textsl{jQuery Conference Boston}, Options for and common issues with automated JavaScript testing, October 2nd, 2011.

  \section{\mysidestyle Posters}
  Bender, J., ``Automatically Identifying Performance Optimizations in jQuery Based JavaScript Applications'', \textsl{Submitted OOPSLA/SPLASHCON}, Identifying a set of morphisms via category theory that can be composed leading to loop fusion, October 19-26th, 2012, \href{http://johnbender.github.com/auto-jquery-optimization-paper/}{\texttt{johnbender.github.com}}\


  % Open Source Contributions
  \section{\mysidestyle Open Source}

  Development lead, jQuery Mobile JavaScript library, \url{www.jquerymobile.com} \vspace{1mm}\\
  Co-creator, Vagrant CLI virtualization tool, \url{www.vagrantup.com}

  % Honors and Awards
  \section{\mysidestyle Honors/Awards}
  National Championship, Men's Division I Volleyball, 2002.\vspace{1mm}\\
  Two Time NCAA National Player of the Week, Men's Division I Volleyball, 2004 \& 2005.\vspace{1mm}\\
  MPSF Honorable Mention, Division I Men's Volleyball, 2005.\vspace{1mm}\\
  Lettered University of Hawai'i, Division I Men's Volleyball, 2001 -- 2005.

  % Computer Skills
  \section{\mysidestyle Programming}
  JavaScript, Ruby, Bash, SQL, Haskell, Python, .NET, Java

  % References
  \section{\mysidestyle References}
  \textsl{available upon request}

\end{resume}
\end{document}
