%______________________________________________________________________________________________________________________
% @brief    LaTeX2e Resume for Kamil K Wojcicki
\documentclass[margin,line]{resume}


%______________________________________________________________________________________________________________________
\begin{document}
\name{\Large John Bender}
\begin{resume}

    %__________________________________________________________________________________________________________________
    % Contact Information
    \section{\mysidestyle Contact\\Information}

    Adobe                            \hfill phone: +1 917 504 3095           \vspace{0mm}\\\vspace{0mm}%
    Web Frameworks Group                          \hfill personal: john.m.bender@gmail.com          \vspace{0mm}\\\vspace{0mm}%
    Design, Web, \& Interactive                          \hfill work: jbender@adobe.com          \vspace{0mm}\\\vspace{0mm}%


    \section{\mysidestyle Research\\Interests}

    Formal Verification, Software Model Checking, Type Systems, Applications of Category Theory


    \section{\mysidestyle Education}

    \textbf{University of Hawai'i at Manoa}, Honolulu, Hawai'i, United States \vspace{2mm}\\\vspace{1mm}%
    \textsl{Bachelors of Science}, Computer Science \hfill \textbf{ August 2001 -- May 2006}\vspace{-3mm}\\\vspace{-1mm}%


    \section{\mysidestyle Research\\Activity}

    \textbf{Automatically Identifying Performance Optimizations in jQuery JavaScript Applications}\\
    \textsl{Paper} \hfill \textbf{Draft}\\
    Motivating statistics, a detailed treatment of the two category definitions and a discussion of the a sample implementation of a library to alert users where optimizations can be found. Further work will include project specific performance data, standard proposal to the jQuery project, and conversion work to the standard.
    \vspace{1mm}\\
    \textsl{Poster} \hfill \textbf{SPLASHCON 2012}\\
    Motivating examples and statistics, using category theory in identifying optimization candidates, the proposed standard, and a sample library implementation.
    \vspace{1mm}\\
    \textsl{Presentation} \hfill \textbf{LA JavaScript, jQCon SF, June -- 2012}\\
    Introduction to category theory, overview of proposed standard, and sample optimizations. Target audience is the jQuery Core development team and advanced jQuery developers.


    \textbf{Middleware as a General Purpose Abstraction}\\
    \textsl{Writing} \hfill \textbf{July, October -- 2010}\\
    Two essays discussing similarities in middleware composition to function composition and the Monad abstractions present in Haskell, including an implementation in the Vagrant command line tool.
    \vspace{1mm}\\
    \textsl{Presentation} \hfill \textbf{LA Ruby Conf, February -- 2012}\\
    Foundational review of WSGI middleware, examples of generality in existing software, and sample refactoring based on generic ``middleware'' in a popular Ruby application.

    %__________________________________________________________________________________________________________________
    % Honours and Awards
    \section{\mysidestyle Honours and\\Awards}

    Best Paper Award, Griffith School of Engineering Research Conference, Nathan, 2007              \vspace{1mm}\\%
    Australian Research Council (ARC) Postgraduate Research Scholarship, Nathan, 2005-2010          \vspace{1mm}\\%
    Scholarship for Outstanding Academic Achievement, Griffith University, Nathan, 2000             \vspace{1mm}\\%
    National Mathematics Summer School, The Australian National University, Canberra, 2000, 1999    \vspace{1mm}\\%
    Certificate of Excellence for Outstanding Academic Achievement, University of Tasmania, 1999    \vspace{1mm}\\%
    Award for Best Design, Electronics Competition, The Electronics Educators Association, 1998


    %__________________________________________________________________________________________________________________
    % Publications
    \section{\mysidestyle Selected Publications}

    Paliwal, K.K., Shannon, B.J., Lyons, J.G. and K.K. W\'ojcicki,
    ``Speech-signal-based frequency warping'',
    \textsl{IEEE Signal Process. Lett.}, Vol. 16, No. 4, pp. 319-322, 2009.

\vspace{-2mm}
    Paliwal, K.K. and K.K. W\'ojcicki,
    ``Effect of analysis window duration on speech intelligibility'',
    \textsl{IEEE Signal Process. Lett.}, Vol. 15, pp. 785-788, 2008.

\vspace{-2mm}
    Stark, A.P., W\'ojcicki, K.K., Lyons, J.G. and K.K. Paliwal,
    ``Noise driven short time phase spectrum compensation procedure for speech enhancement'',
    In \textsl{Proc. INTERSPEECH}, pp. 549-552, 2008.

\vspace{-2mm}
    W\'ojcicki, K.K., Milacic, M., Stark, A.P., Lyons, J.G. and K.K. Paliwal,
    ``Exploiting conjugate symmetry of the short-time Fourier spectrum for speech enhancement'',
    \textsl{IEEE Signal Process. Lett.}, Vol. 15, pp. 461-464, 2008.

\vspace{-2mm}
    W\'ojcicki, K.K. and K.K. Paliwal,
    ``Importance of the dynamic range of an analysis window function for phase-only and magnitude-only reconstruction of speech'',
    In \textsl{Proc. ICASSP}, pp. 729-733, 2007.



    %__________________________________________________________________________________________________________________
    % Professional Experience
    \section{\mysidestyle Professional\\Experience}

    \textbf{Griffith University}, Nathan, Queensland, Australia \vspace{2mm}\\\vspace{1mm}%
    \textsl{Teaching Assistant} \hfill \textbf{February 2005 -- present}\\
    Teaching assistant for undergraduate courses in electrical engineering,
    including signals and systems, digital signal processing,
    statistical signal processing and Unix systems.
    Examination invigilator for undergraduate as well as graduate courses.


    \textbf{Hewlett Packard}, Milton, Queensland, Australia \vspace{2mm}\\\vspace{1mm}%
    \textsl{Server Specialist} \hfill \textbf{March 2008 -- present}\\
    Enterprise data center deployments, relocation and servicing
    for clients such as Cement Australia, Gold Coast City Council, Queensland Health,
    Queensland Investment Corporation (QIC), Queensland Ombudsman's Office and Bain Gasteen Lawyers.

    \textsl{Field Services Engineer} \hfill \textbf{June 2004 -- present}\vspace{1.5mm}\\\vspace{0mm}%
    Workstation deployments for clients such as AMCOR,
    Blake Dawson Waldron, Bank of Queensland, Pindara Private Hospital and others.

    \textbf{Fujitsu Australia}, Newstead, Queensland, Australia \vspace{2mm}\\\vspace{1mm}%
    \textsl{Field Services Engineer} \hfill \textbf{April 2002 -- December 2003}\\
    Point-of-sale deployments for various clients,
    including Queensland Transport, Coles, Woolworths and Commonwealth Bank business centers.



    %__________________________________________________________________________________________________________________
    % Computer Skills
    \section{\mysidestyle Programming}

    C, C++, Matlab, Linux shell scripting, Perl, Python, \LaTeXe, PBS, SQL, Java, .NET, SPSS.



    %__________________________________________________________________________________________________________________
    % Referees
%    \section{\mysidestyle Referees}
%    {\sl Available on request.}



%______________________________________________________________________________________________________________________
\section{\mysidestyle Referees}

\begin{tabular}{@{}p{6cm}p{6cm}}
\textbf{Professor Kuldip Paliwal}       &  \textbf{Dr Stephen So}                   \\
Professor                               &  Associate Lecturer                       \\
Griffith University                     &  Griffith University                      \\
Nathan, Queensland, Australia           &  Gold Coast, Queensland, Australia        \\
phone: \textsl{available on request}    &  phone: \textsl{available on request}     \\
e-mail: \textsl{available on request}   &  e-mail: \textsl{available on request}    \\
\end{tabular}

\begin{tabular}{@{}p{6cm}p{6cm}}
\textbf{Dr Conrad Sanderson}            &  \textbf{Mr Sean Loye}                    \\
Researcher                              &  Systems Engineer                         \\
National ICT Australia                  &  Hewlett Packard                          \\
St Lucia, Queensland, Australia         &  Milton, Queensland, Australia            \\
phone: \textsl{available on request}    &  phone: \textsl{available on request}     \\
e-mail: \textsl{available on request}   &  e-mail: \textsl{available on request}    \\
\end{tabular}



%______________________________________________________________________________________________________________________
\end{resume}
\end{document}


%______________________________________________________________________________________________________________________
% EOF

